\chapter{Elicitation/Background - Interview Questions}
\label{app:intquest}

\textbf{Introduction}\\
A presentation of the background, content and purpose of the interview.
\begin{enumerate}
\item \textbf{Personal information}
\begin{enumerate}
\item Present who you are and your background?
\item What is your role (in the company)?
\item What is your role as a SystemWeaver user?
\end{enumerate}

\item \textbf{SystemWeaver usage}
\begin{enumerate}
\item For how long have you been using SystemWeaver?
\item How do you use SystemWeaver?
\item What do you experience as the advantages with the product?
\item What do you experience as obstacles using the product?
\item Have you tried other requirement management software?\\
If so, what do you feel is the main difference between SystemWeaver and those?\\
If not, why?
\end{enumerate}

\item \textbf{Requirement management}
\begin{enumerate}
\item What information do you provide to the documentation?
\item What information do you use in the documentation?
\item Do you have a structured way of working with requirements?
\item How often do you feel a need of change in the documentation (i.e.\ in which situations do you observe that you need to do changes/additions/comments to requirement documentation, design-documents, etc)?
\item What are the causes for these changes? (i.e.\ the requirement is wrong, it is poor stated, it is ambiguous or simply wrong etc.)
\item When does these changes/additions/comments happen? (i.e.\ are you going through the documentation after you have been doing your task or are you doing them in parallel?)
\item When would you like these changes to occur?
\item What information do you think a requirement should contain?
\item How are other people affected based on your contribution to the requirements and documentation?
\item How do you assess the quality of the requirements?
\end{enumerate}

\item \textbf{Voice Recognition Software}
\begin{enumerate}
\item Have you tried any speech control applications 
\item What do think about it/them? / Why are you not using it?
\end{enumerate}

\item \textbf{Open question}
\begin{enumerate}
\item Do you have any questions? 
\item Is there something you would like to add?
\end{enumerate}

\end{enumerate}











